SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-01-23 scipy-1.0/paper.tex
MAINT: provide likely explanation for performance regression in Fig. S1.
MAINT: cite PyCBC usage for LIGO project.

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts imported three different SciPy submodules: signal processing,
interpolation, and input/output.  SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  SciPy is built on top of NumPy, and is itself the foundation
upon which higher level scientific libraries, including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.

>>>>

SciPy is a library of numerical routines for the Python programming
language, providing the fundamental building blocks for modeling and
solving scientific problems.  For example, when LIGO, the Laser
Interferometer Gravitational-Wave Observatory, recently announced the
discovery of gravitational waves, their published Python analysis
scripts\cite{LIGO-open,alex_nitz_2018_1596771,GW150914-Python} 
imported many different SciPy submodules for: signal processing,
interpolation, input / output, optimization, statistics, integration,
and more. SciPy has routines for solving
classes of generic problems such as optimization, integration,
interpolation, eigenvalues, and linear systems.  It also provides
specialized data structures, such as sparse arrays and k-dimensional
trees.  SciPy is built on top of NumPy, and is itself the foundation
upon which higher level scientific libraries, including scikit-learn\cite{pedregosa2011scikit}
and scikit-image\cite{vanderwalt2014scikit}, are built.
